\chapter{Complete dataset description} \label{app:A}

The \textit{Olympic Games Medals 1986-2022} dataset, sourced from Kaggle \cite{olympic_19862022}, contains comprehensive information about the Olympic Games spanning from 1986 to 2022. The data, originally scraped from the official International Olympic Committee website \cite{olympics}, includes details about athletes, medal results, hosting nations, and events. This section provides a complete overview of the dataset structure and its attributes.

The dataset consists of multiple files, each focusing on specific aspects of the Olympic Games. The key files and their contents are described below.

\section{olympic\_athletes.csv}

The file \texttt{olympic\_athletes.csv} includes the following attributes:

\begin{itemize}
    \item \texttt{athlete\_url}: The URL linking to the athlete's profile on the official Olympics website.
    \item \texttt{athlete\_full\_name}: The full name of the athlete.
    \item \texttt{games\_participations}: The total number of Olympic Games in which the athlete participated.
    \item \texttt{first\_game}: The first Olympic Games in which the athlete competed, specified by city and year.
    \item \texttt{athlete\_year\_birth}: The birth year of the athlete.
    \item \texttt{athlete\_medals}: The total medals won by the athlete across all participations.
    \item \texttt{bio}: A brief biographical summary or description of the athlete, if available, which is often not the case.
\end{itemize}

\section{olympic\_medals.csv}

The file \texttt{olympic\_medals.csv} includes the following attributes:

\begin{itemize}
    \item \texttt{discipline\_title}: The title of the sport or discipline (e.g., \texttt{Swimming}, \texttt{Athletics}).
    \item \texttt{slug\_game}: A unique identifier for the specific Olympic Games (e.g., \texttt{barcelona-1992}).
    \item \texttt{event\_title}: The title of the specific event within the discipline (e.g., \texttt{5000m men}, \texttt{parallel bars men}).
    \item \texttt{event\_gender}: The gender category of the event (\texttt{Men}, \texttt{Women}, or \texttt{Mixed} for mixed events).
    \item \texttt{medal\_type}: The type of medal awarded (\texttt{GOLD}, \texttt{SILVER}, or \texttt{BRONZE}).
    \item \texttt{participant\_type}: The type of participant (e.g., \texttt{Athlete} if individual, \texttt{GameTeam} otherwise).
    \item \texttt{participant\_title}: The name or title of the participant (e.g., team name or athlete name).
    \item \texttt{athlete\_url}: The URL linking to the athlete's profile (if applicable).
    \item \texttt{athlete\_full\_name}: The full name of the athlete (if applicable).
    \item \texttt{country\_name}: The name of the country associated with the medal-winning participant.
    \item \texttt{country\_code}: The two-letter country code (ISO 3166-1 alpha-2).
    \item \texttt{country\_3\_letter\_code}: The three-letter country code (ISO 3166-1 alpha-3).
\end{itemize}

\section{olympic\_hosts.csv}

The file \texttt{olympic\_hosts.csv} includes the following attributes:

\begin{itemize}
    \item \texttt{game\_slug}: A unique identifier for the specific Olympic Games (e.g., \texttt{barcelona-1992}).
    \item \texttt{game\_end\_date}: The end date of the Olympic Games.
    \item \texttt{game\_start\_date}: The start date of the Olympic Games.
    \item \texttt{game\_location}: The location of the Olympic Games (country).
    \item \texttt{game\_name}: The official name of the Olympic Games (e.g., \texttt{Oslo 1952}).
    \item \texttt{game\_season}: The season of the Games (\texttt{Summer} or \texttt{Winter}).
    \item \texttt{game\_year}: The year in which the Olympic Games took place.
\end{itemize}

\section{olympic\_results.csv}

The file \texttt{olympic\_results.csv} includes the following attributes:

\begin{itemize}
    \item \texttt{discipline\_title}: The title of the sport or discipline (e.g., \texttt{Swimming}, \texttt{Athletics}).
    \item \texttt{event\_title}: The title of the specific event within the discipline (e.g., \texttt{5000m men}, \texttt{tempest mixed}).
    \item \texttt{slug\_game}: A unique identifier for the specific Olympic Games (e.g., \texttt{montreal-1976}).
    \item \texttt{participant\_type}: The type of participant (e.g., \texttt{Athlete} if individual, \texttt{GameTeam} otherwise).
    \item \texttt{medal\_type}: The type of medal awarded (\texttt{GOLD}, \texttt{SILVER}, \texttt{BRONZE}, or \texttt{None} for participants who did not win a medal).
    \item \texttt{athletes}: A list of athletes associated with the participant (useful for team events).
    \item \texttt{rank\_equal}: Whether the rank is shared among multiple participants (\texttt{True} or \texttt{False}), if applicable.
    \item \texttt{rank\_position}: The rank of the participant in the event.
    \item \texttt{country\_name}: The name of the country associated with the participant.
    \item \texttt{country\_code}: The two-letter country code (ISO 3166-1 alpha-2).
    \item \texttt{country\_3\_letter\_code}: The three-letter country code (ISO 3166-1 alpha-3).
    \item \texttt{athlete\_url}: The URL linking to the athlete's profile (if applicable).
    \item \texttt{athlete\_full\_name}: The full name of the athlete (if applicable).
    \item \texttt{value\_unit}: The unit of measurement for performance values (e.g., seconds, meters).
    \item \texttt{value\_type}: The type of performance value recorded (e.g., time, distance).
\end{itemize}

\section{Dataset Summary}

The dataset provides detailed information about:
\begin{itemize}
    \item Over 120 years of Olympic Games history, spanning Summer and Winter Games.
    \item Thousands of athletes from different countries, disciplines, and events.
    \item Medal counts and distribution patterns across various sports and seasons.
    \item Host cities and countries, offering geographical insights into the Games.
\end{itemize}
